Changelog

### 2021-05-24 changelog.tex
Updates from Overleaf

\maketitle
Thank you for reviewing my dissertation. I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flow and fix all the typos and grammar errors. In summary, the revisions cover the following aspects.

@@

I have a few choices. First, I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still generates plenty of false positives.

On the other hand, there are many successful stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.

\item \textbf{Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.}
\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}

>>>>

\maketitle
Thank you for reviewing my dissertation. I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flows and fix all the typos and grammar errors. In summary, the revisions cover the following aspects.

@@

I have a few choices to address the limitations. First, I can use static analysis (model checking or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are several papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years. In particular, I find fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016.

\item \textbf{Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.}

Like many other research projects,

\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}
